The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-11-15 paper/simplest_effects.tex
fix typos
add bibtex citations; update model #4 figure

We return to our group of binarity-ignoring astronomers. They do 
not know the true rate density~--~they would like to discover it!
In their signal-to-noise limited transit survey, they select stars 
that they think can yield transit detections.
Since the noise is Poissonian, they assume
\begin{equation}
\frac{{\rm signal}}{{\rm noise}}
\propto \frac{(r/R)^2}{F^{-1/2}}
\propto F^{1/2}
\propto L_{\rm sys}^{1/2} d^{-1}, \quad ({\rm incorrectly\ assumed})
\end{equation}
for $R$ the constant stellar radius, $F$ the photon flux, $L_{\rm sys}$ the 
luminosity of a system, and $d$ its distance from us.
At fixed planet radius, semimajor axis, stellar radius, and stellar luminosity,
a constant signal-to-noise floor yields a maximum detectable 
distance (Pepper et al 2003, Pepper and Gaudi 2005).
The maximum distance out to which our binarity-ignoring astronomers 
select stars, $d_{\rm sel}$, thus scales as $L_{\rm sys}^{1/2}$.

@@

To assess the severity of these errors, we need to make assumptions about the 
stellar and planetary populations.
The important quantity for the stellar population is $N_1/N_0$, the ratio of 
selected primaries (or binaries) to singles. We can define
\begin{align}
\mu \equiv \frac{N_1}{N_0} &=
\frac{n_b}{n_s} \left(\frac{d_{\rm sel,b}}{d_{\rm sel,s}}\right)^3 = 
\frac{{\rm BF}}{1-{\rm BF}} (1+\ell)^{3/2},
\label{eq:mu_definition}
\end{align}
where $n_b$ and $n_s$ are the number density of binaries and singles in a 
volume limited sample, and the maximum selected distance for binary and single 
systems are $d_{\rm sel,b}$ and $d_{\rm sel,s}$.
The light ratio $\ell$ is defined relative to the primary, so that
$L_{\rm sys} = L_1(1+\ell)$.
The binary fraction in a volume limited sample is ``{\rm BF}''.
For instance, Raghavan et al., (2010) found a multiplicity fraction\footnote{
    The binary fraction is the fraction of systems in a volume-limited sample 
    that are binary. It is equivalent to the multiplicity fraction if there 
    are no triple, quadruple, or higher order multiples. In that case, ${\rm 
        BF} = n_b / (n_s+n_b)$.
} of 0.44 for primaries with masses from $0.7M_\odot$ to $1.3M_\odot$. 
``Twin binaries'' are perhaps 10-20\% of the binaries in a volume-limited 
sample, depending on how ``twin'' is defined.
Thus a representative twin binary fraction for this model is ${\rm BF}\approx 
0.05$-$0.1$.

@@

An alternative assumption is that secondaries do not host planets. In that 
case, $Z_0=Z_1$, and $Z_2=0$. The correction to the rate density at the true 
planet radius becomes
\begin{equation}
X_\Gamma(r_p) = \frac{1+2\mu}{(1+\mu)^2}.
\end{equation}
This evaluates to 0.95 if ${\rm BF}=0.1$, and 0.99 if ${\rm BF}=0.05$.
While it is hard to justify the assumption that secondaries are planet-less, 
it is worth noting that $\Gamma_a/\Gamma$ is sensitive to the relative number 
of planets per single, primary, and secondary.

>>>>

We return to our group of binarity-ignoring astronomers. They do 
not know the true rate density~--~they would like to discover it!
In their signal-to-noise limited transit survey, they select stars 
that they think can yield transit detections.
Since the noise is Poissonian, they assume
\begin{equation}
\frac{{\rm signal}}{{\rm noise}}
\propto \frac{(r/R)^2}{F^{-1/2}}
\propto F^{1/2}
\propto L_{\rm sys}^{1/2} d^{-1}, \quad ({\rm incorrectly\ assumed})
\end{equation}
for $R$ the constant stellar radius, $F$ the photon flux, $L_{\rm sys}$ the 
luminosity of a system, and $d$ its distance from us.
At fixed planet radius, semimajor axis, stellar radius, and stellar luminosity,
a constant signal-to-noise floor yields a maximum detectable 
distance~\citep{pepper_using_2003,pepper_searching_2005}.
The maximum distance out to which our binarity-ignoring astronomers 
select stars, $d_{\rm sel}$, thus scales as $L_{\rm sys}^{1/2}$.

@@

To assess the severity of these errors, we need to make assumptions about the 
stellar and planetary populations.
The important quantity for the stellar population is $N_1/N_0$, the ratio of 
selected primaries (or binaries) to singles. We can define
\begin{align}
\mu \equiv \frac{N_1}{N_0} &=
\frac{n_b}{n_s} \left(\frac{d_{\rm sel,b}}{d_{\rm sel,s}}\right)^3 = 
\frac{{\rm BF}}{1-{\rm BF}} (1+\ell)^{3/2},
\label{eq:mu_definition}
\end{align}
where $n_b$ and $n_s$ are the number density of binaries and singles in a 
volume limited sample, and the maximum selected distance for binary and single 
systems are $d_{\rm sel,b}$ and $d_{\rm sel,s}$.
The light ratio $\ell$ is defined relative to the primary, so that
$L_{\rm sys} = L_1(1+\ell)$.
The binary fraction in a volume limited sample is ``{\rm BF}''.
For instance, \citet{raghavan_survey_2010} found a multiplicity 
fraction\footnote{
    The binary fraction is the fraction of systems in a volume-limited sample 
    that are binary. It is equivalent to the multiplicity fraction if there 
    are no triple, quadruple, or higher order multiples. In that case, ${\rm 
        BF} = n_b / (n_s+n_b)$.
} of 0.44 for primaries with masses from $0.7M_\odot$ to $1.3M_\odot$. 
``Twin binaries'' are perhaps 10-20\% of the binaries in a volume-limited 
sample, depending on how ``twin'' is defined.
Thus a representative twin binary fraction for this model is ${\rm BF}\approx 
0.05$-$0.1$.

@@

An alternative assumption is that secondaries do not host planets. In that 
case, $Z_0=Z_1$, and $Z_2=0$. The correction to the rate density at the true 
planet radius becomes
\begin{equation}
X_\Gamma(r_p) = \frac{1+2\mu}{(1+\mu)^2}.
\end{equation}
This evaluates to 0.94 if ${\rm BF}=0.1$, and 0.98 if ${\rm BF}=0.05$.
While it is hard to justify the assumption that secondaries are planet-less, 
it is worth noting that $\Gamma_a/\Gamma$ is sensitive to the relative number 
of planets per single, primary, and secondary.
